\papertitle

### 2021-03-04 source_separation/paper/paper.tex
Add to table
Add BBC reference

% Authors
% Please note that submissions are NOT anonymous, therefore 
% authors' names have to be VISIBLE in your manuscript. 
% Authors are entered as an ordered list, each one can be linked to multiple affiliations using the correct index.
% Available tags for authors are: \firstname \middlename \lastname \generation \originalname \email \orcid
% Available tags for affiliations are: \unit \department \institution \streetaddress \city \state \postcode \country \type
% type can take as value: University, Company, Music, Independent, Other
%
% \author[]{\mbox{\firstname{}\middlename{}\lastname{}\originalname{}\generation{}\email{}\orcid{}}}
% mbox force an author not to be split over multiple lines
\author[1]{\mbox{\firstname{Carmine}\lastname{Cella}}}
\author[1]{\mbox{\firstname{Luke}\lastname{Dzwonczyk}}}

@@

		\subsection{Data}
		We created our own targets as combinations of four sub-targets. The sub-targets come from the NIGENS \cite{NIGENS} and BBC \cite{} databases, and freesound.org \cite{freesound}. We selected a total of 90 samples from these databases, choosing sounds that fit the following criteria:

@@

	\begin{table}[t]
		\begin{center}
			\begin{tabular}{|c|c|}
				\hline
				& Average distance \\
				\hline
				Full target & 25.73 \\
				\hline
				TDCNN++ & 25.44 \\
				\hline
				Demucs & 27.62 \\
				\hline
				NMF & 22.32 \\
				\hline
				Ground truth & 24.27 \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Average across \textbf{X} targets showing the distance between target and orchestration for various methods. "Full target" means no separation was performed. }
		\label{tab:distances}
	\end{table}

>>>>

% Authors
% Please note that submissions are NOT anonymous, therefore 
% authors' names have to be VISIBLE in your manuscript. 
% Authors are entered as an ordered list, each one can be linked to multiple affiliations using the correct index.
% Available tags for authors are: \firstname \middlename \lastname \generation \originalname \email \orcid
% Available tags for affiliations are: \unit \department \institution \streetaddress \city \state \postcode \country \type
% type can take as value: University, Company, Music, Independent, Other
%
% \author[]{\mbox{\firstname{}\middlename{}\lastname{}\originalname{}\generation{}\email{}\orcid{}}}
% mbox force an author not to be split over multiple lines
\author[1]{\mbox{\firstname{Carmine}\lastname{Cella}}}
\author[1]{\mbox{\firstname{Luke}\lastname{Dzwonczyk}\email{dz.luke@berkeley.edu}}}

@@

		\subsection{Data}
		We created our own targets as combinations of four sub-targets. The sub-targets come from the NIGENS \cite{NIGENS} and BBC \cite{BBC} databases, and freesound.org \cite{freesound}. We selected a total of 90 samples from these databases, choosing sounds that fit the following criteria:

@@

	\begin{table}[t]
		\begin{center}
			\begin{tabular}{|c|c|}
				\hline
				& Average distance \\
				\hline
				Full target & 25.73 \\
				\hline
				TDCNN & \\
				\hline
				TDCNN++ & 25.44 \\
				\hline
				Demucs & 27.62 \\
				\hline
				OpenUnmix & \\
				\hline
				NMF & 22.32 \\
				\hline
				Ground truth & 24.27 \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Average across \textbf{X} targets showing the distance between target and orchestration for various methods. "Full target" means no separation was performed. }
		\label{tab:distances}
	\end{table}
